Multisensor Architecture for an Intersection Management System

### 2018-06-01 ch3-arch_sys.tex
updated laser_bg_remove figure
Added bg_model description

\begin{table}[ht!]
\footnotesize
\centering
\begin{tabular}{|c | p{8cm}|}
\hline
\textbf{Name} & \textbf{Description} \\
\hline
laser\_pol\_msg & Contains a timestamp, an array of N angles and and array of N measurements \\
\hline
laser\_cart\_msg & Contains a timestamp, an array of N (x, y) coordinates \\
\hline
laser\_cfg & Contains position and orientation information, also has a background model for the laser sensor \\
\hline
occgrid\_msg & Contains a timestamp and an occupancy grid in the form of an MxN array \\
\hline
\end{tabular}
\caption{Description of diferent types of messages and parameters used}
\label{desc_map}
\end{table}

@@

\subsubsection{Preprocessing}
\begin{description}
\item[laser\_background\_remove]laser\_bg\_remove
\begin{figure}[ht!]
\centering
\includegraphics[scale=0.7]{fig/3/laser_bg_remove.pdf}
\caption{laser\_bg\_remove}
\label{laser_bg_remove}
\end{figure}

>>>>

\begin{table}[ht!]
\footnotesize
\centering
\begin{tabular}{|c | p{8cm}|}
\hline
\textbf{Name} & \textbf{Description} \\
\hline
laser\_pol\_msg & Contains a timestamp, an array of N angles and and array of N measurements \\
\hline
laser\_cart\_msg & Contains a timestamp, an array of N (x, y) coordinates \\
\hline
laser\_cfg & Contains position and orientation information, also has a background model for the laser sensor \\
\hline
occgrid\_msg & Contains a timestamp and an occupancy grid in the form of an MxN array \\
\hline
occgrid\_cfg & Contains occupancy grid configuration for the scene \\
\hline
\end{tabular}
\caption{Description of diferent types of messages and parameters used}
\label{desc_map}
\end{table}

@@

\subsubsection{Preprocessing}
\begin{description}
\item[laser\_background\_remove]laser\_bg\_remove

This block takes as input a message of type laser\_pol\_msg, which contains raw readings from laser sensor. Also, it takes a laser\_cfg parameter which includes a background model for the laser sensor, generated from a set of scans and taking the maximum measurement in each angle of scanning, defined as follows:

Let suppose we have N scans from the laser and $d_{\theta i}$ be the distance measure at angle $\theta$ in scan $i$. Thus, the background value for that angle $\theta$ is $bg_\theta = max( \{d_{\theta i} | 1 < i < N\})$ and the background model is $bg = \{bg_\theta | \theta \in \Theta\} $ where $\Theta$ is the set of angles of scanning, in this case from -90\degree to 90\degree with 0.5\degree step.
\begin{figure}[ht!]
\centering
\includegraphics[scale=0.7]{fig/3/laser_bg_remove.pdf}
\caption{laser\_bg\_remove}
\label{laser_bg_remove}
\end{figure}
